---
title: "Week 3 Peer Review"
output: html_document
---

```{r setup, include=FALSE}

######DO NOT MODIFY. This will load required packages and data.

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

cces <- drop_na(read_csv(url("https://www.dropbox.com/s/ahmt12y39unicd2/cces_sample_coursera.csv?raw=1")))

cel <- drop_na(read_csv(url("https://www.dropbox.com/s/4ebgnkdhhxo5rac/cel_volden_wiseman%20_coursera.csv?raw=1")))

```

Following the directions on the Coursera assignment page, you will make four original visualizations. Note that the data for the CCES and CEL data are imported in code in the R Markdown file.

### Put your name here: Iqman Singh Bhatia

## Exercise 1

Explain what you are visualizing here: No of Bills Passed vs Vote Percentage of 100th Congress

Put your figure here:

```{r exercise1,echo=T}

cong100 = cel[cel$congress==100,]
cong100 = rename(cong100,Gender = female)
cong100$Gender[cong100$Gender == 0]="Male"
cong100$Gender[cong100$Gender == 1]="Female"
head(cong100)
ggplot(data = cong100,aes(y=all_pass,x=votepct,color=Gender))+geom_jitter()+labs(title = "No of Bills Passed vs Vote Percentage of 100th Congress",x="Vote Percentafe",y="Bills Passed")  

```

## Exercise 2

Explain what you are visualizing here:

Put your figure here: Region vs Income

```{r exercise2,echo=T}
ggplot(data=cces,aes(x=region,y=faminc_new,group=region))+geom_boxplot()+labs(title = "Region vs Income" ,x="Region of Residence",y="Family Income ")
  
```

## Exercise 3

Explain what you are visualizing here: Education Loan vs Income

Put your figure here:

```{r exercise3,echo=T}
ggplot(data=cces,aes(x=edloan,y=faminc_new,group=edloan))+geom_boxplot()+labs(title = "Education Loan vs Income" ,x="Education Loan",y="Family Income ")

```

## Exercise 4

Explain what you are visualizing here: Bills Passed vs Vote Percent of Democrats or Republicans

Put your figure here:

```{r exercise4,echo=T}
cong100$majority[cong100$majority == 0] = "Minority"
cong100$majority[cong100$majority == 1] = "Majority"
cong100$dem[cong100$dem == 0]="Republican"
cong100$dem[cong100$dem == 1]="Democrat"

ggplot(data=cong100,aes(x=votepct,y=all_pass,color=dem))+geom_jitter()+labs(title="Bills Passed vs Vote Percent of Democrats or Republicans",x="Vote Percentage",y="Bills Passed") + facet_grid(cols = vars(dem))

```
